---
title: "HARGA BATU BARA"
author: "Rafisal Hamdi"
date: "18/3/2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

# Library

```{r}
library(caret)
library(mlbench)
library(MASS)
library(corrplot)
library(dplyr)
library(MLmetrics)
library(writexl)
library(brnn)
library(Metrics)

mape <- function(actual,pred){
  mape <- mean(abs((actual - pred)/actual))*100
  return (mape)
}
```

# Dataframe

```{r}
library(readxl)
df <- read_excel("Dataset.xlsx")
View(df)
```

# Numeric dan Factor

```{r}
df$period = as.numeric(df$period)
df$month = as.factor(df$month)
df$price_prev_1 = as.numeric(df$price_prev_1)
df$price_prev_2 = as.numeric(df$price_prev_2)
df$price_prev_3 = as.numeric(df$price_prev_3)
df$price_prev_4 = as.numeric(df$price_prev_4)
df$price_prev_5 = as.numeric(df$price_prev_5)
df$price_prev_6 = as.numeric(df$price_prev_6)
df$price_prev_7 = as.numeric(df$price_prev_7)
df$price_prev_8 = as.numeric(df$price_prev_8)
df$price_prev_9 = as.numeric(df$price_prev_9)
df$price_prev_10 = as.numeric(df$price_prev_10)
df$price_prev_11 = as.numeric(df$price_prev_11)
df$price_prev_12 = as.numeric(df$price_prev_12)
df$price = as.numeric(df$price)
summary(df)
```

# Dummy

```{r}
library(fastDummies)

# Create dummy variables:
df <- dummy_cols(df, select_columns = 'month')
View(df)
```

# Splitting Data

```{r}
df_train = df[1:130,-2]
df_test = df[131:154,-2]
```

# View Data

```{r}
View(df_train)
View(df_test)
```

# LM_Training
## LM_Preproc_None
```{r}
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = TRUE)
fit.lm1<- train(price~., data=df_train, 
                method="lm", metric="RMSE", trControl=control)
# summarize fit
print(fit.lm1)

#prediction
lm_pred1_train <- predict(fit.lm1, newdata = df_train)
print(lm_pred1_train)
#Find MAPE
MAPE.lm1_train <- MAPE(lm_pred1_train , y_true = df_train$price)
print(MAPE.lm1_train)
```

## LM_Preproc_Scale & Center
```{r}
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = TRUE)
fit.lm2<- train(price~., data=df_train, 
                method="lm", metric="RMSE", 
                preProcess=c("center", "scale"), trControl=control)
# summarize fit
print(fit.lm2)

#prediction
lm_pred2_train <- predict(fit.lm2, newdata = df_train)
print(lm_pred2_train)
#Find MAPE
MAPE.lm2_train <- MAPE(lm_pred2_train , y_true = df_train$price)
print(MAPE.lm2_train)
```

# LM_Testing
```{r}
#Preprocessing-None
lm_pred1_test <- predict(fit.lm1, df_test)
lm_pred1_test

error1.lm <- df_test$price - lm_pred1_test
RMSE1.lm <- sqrt(mean(error1.lm^2))
print(RMSE1.lm)

#Find MAPE
MAPE.lm1_test <- MAPE(lm_pred1_test , y_true = df_test$price)
print(MAPE.lm1_test)
```

```{r}
#Preprocessing-Scale & Center
lm_pred2_test <- predict(fit.lm2, df_test)
lm_pred2_test

error2.lm <- df_test$price - lm_pred2_test
RMSE2.lm <- sqrt(mean(error2.lm^2))
print(RMSE2.lm)

#Find MAPE
MAPE.lm2_test <- MAPE(lm_pred2_test , y_true = df_test$price)
print(MAPE.lm2_test)
```


# EN_Training 
## Elastic Net_Preprocessing-None

```{r}
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = TRUE)
fit.en1<- train(price~., data=df_train, method="glmnet", metric="RMSE", trControl=control)
# summarize fit
print(fit.en1)

#prediction
en_pred1_train <- predict(fit.en1, newdata = df_train)
print(en_pred1_train)
#Find MAPE
MAPE.en1_train <- MAPE(en_pred1_train , y_true = df_train$price)
print(MAPE.en1_train)
```

## Elastic Net_Preprocessing-Center & Scale

```{r}
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = TRUE)
fit.en2<- train(price~., data=df_train, method="glmnet", metric="RMSE", preProcess=c("center", "scale"), trControl=control)
# summarize fit
print(fit.en2)

#prediction
en_pred2_train <- predict(fit.en2, newdata = df_train)
print(en_pred2_train)
#Find MAPE
MAPE.en2_train <- MAPE(en_pred2_train , y_true = df_train$price)
print(MAPE.en2_train)
```

# EN_Testing

```{r}
#Preprocessing-None
en_pred1_test <- predict(fit.en1, df_test)
en_pred1_test

error1.en <- df_test$price - en_pred1_test
RMSE1.en <- sqrt(mean(error1.en^2))
print(RMSE1.en)

#Find MAPE
MAPE.en1_test <- MAPE(en_pred1_test , y_true = df_test$price)
print(MAPE.en1_test)
```

```{r}
#Preprocessing-Scale & Center
en_pred2_test <- predict(fit.en2, df_test)
en_pred2_test

error2.en <- df_test$price - en_pred2_test
RMSE2.en <- sqrt(mean(error2.en^2))
print(RMSE2.en)

#Find MAPE
MAPE.en2_test <- MAPE(en_pred2_test , y_true = df_test$price)
print(MAPE.en2_test)
```

# SVM_Training

## Support Vector Machine_Preprocessing-None

```{r}
library(LiblineaR)
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)
fit.svm1<- train(price~.,data=df_train, method="svmLinear3", metric="RMSE", trControl=control)
# summarize fit
print(fit.svm1)

#prediction
svm_pred1_train <- predict(fit.svm1, newdata = df_train)
print(svm_pred1_train)
#Find MAPE
MAPE.svm1_train <- MAPE(svm_pred1_train , y_true = df_train$price)
print(MAPE.svm1_train)
```

## Support Vector Machine_Preprocessing-Center & Scale

```{r}
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)
fit.svm2<- train(price~.,data=df_train, method="svmLinear3", metric="RMSE", preProcess=c("center", "scale"), trControl=control)
# summarize fit
print(fit.svm2)

#prediction
svm_pred2_train <- predict(fit.svm2, newdata = df_train)
print(svm_pred2_train)
#Find MAPE
MAPE.svm2_train <- MAPE(svm_pred2_train , y_true = df_train$price)
print(MAPE.svm2_train)
```

# SVM_Testing

```{r}
#Preprocessing-None
svm_pred1_test <- predict(fit.svm1, df_test)
svm_pred1_test

error1.svm <- df_test$price - svm_pred1_test
RMSE1.svm <- sqrt(mean(error1.svm^2))
print(RMSE1.svm)

#Find MAPE
MAPE.svm1_test <- MAPE(svm_pred1_test , y_true = df_test$price)
print(MAPE.svm1_test)
```

```{r}
#Preprocessing-Scale & Center
svm_pred2_test <- predict(fit.svm2, df_test)
svm_pred2_test

error2.svm <- df_test$price - svm_pred2_test
RMSE2.svm <- sqrt(mean(error2.svm^2))
print(RMSE2.svm)

#Find MAPE
MAPE.svm2_test <- MAPE(svm_pred2_test , y_true = df_test$price)
print(MAPE.svm2_test)
```

# NN_Training

## Neural Networks_Preprocessing-None

```{r}
library(brnn)

control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)
fit.nn1 <- train(price~., data=df_train,
                 method="brnn", metric="RMSE", trControl=control)
print(fit.nn1)

#prediction
nn_pred1_train <- predict(fit.nn1, newdata = df_train)
print(nn_pred1_train)
#Find MAPE
MAPE.nn1_train <- MAPE(nn_pred1_train , y_true = df_train$price)
print(MAPE.nn1_train)
```

## Neural Networks_Preprocessing-Center & Scale

```{r}
library(brnn)
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)
fit.nn2<- train(price~.,data=df_train, method="brnn",
                metric="RMSE", preProcess=c("center", "scale"),
                trControl=control)

print(fit.nn2)

#prediction
nn_pred2_train <- predict(fit.nn2, newdata = df_train)
print(nn_pred2_train)
#Find MAPE
MAPE.nn2_train <- MAPE(nn_pred2_train , y_true = df_train$price)
print(MAPE.nn2_train)
```

# NN_Testing

```{r}
#Preprocessing-None
nn_pred1_test <- predict(fit.nn1, df_test)
nn_pred1_test

error1.nn <- df_test$price - nn_pred1_test
RMSE1.nn <- sqrt(mean(error1.nn^2))
print(RMSE1.nn)

#Find MAPE
MAPE.nn1_test <- MAPE(nn_pred1_test , y_true = df_test$price)
print(MAPE.nn1_test)
```

```{r}
#Preprocessing-Scale & Center
nn_pred2_test <- predict(fit.nn2, df_test)
nn_pred2_test

error2.nn <- df_test$price - nn_pred2_test
RMSE2.nn <- sqrt(mean(error2.nn^2))
print(RMSE2.nn)

#Find MAPE
MAPE.nn2_test <- MAPE(nn_pred2_test , y_true = df_test$price)
print(MAPE.nn2_test)
```


# GBM_Training
## GBM_Preproc_None
```{r}
library(xgboost)

control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)
fit.gbm1 <- train(price~., data=df_train,
                 method="xgbLinear", metric="RMSE", trControl=control)
print(fit.gbm1)

#prediction
gbm_pred1_train <- predict(fit.gbm1, newdata = df_train)
print(gbm_pred1_train)
#Find MAPE
MAPE.gbm1_train <- MAPE(gbm_pred1_train , y_true = df_train$price)
print(MAPE.gbm1_train)
```


## GBM_Preproc_Scale & Center
```{r}
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)
fit.gbm2 <- train(price~., data=df_train,
                  method="xgbLinear", metric="RMSE", 
                  preProcess=c("center", "scale"), trControl=control)
print(fit.gbm2)

#prediction
gbm_pred2_train <- predict(fit.gbm2, newdata = df_train)
print(gbm_pred2_train)
#Find MAPE
MAPE.gbm2_train <- MAPE(gbm_pred2_train , y_true = df_train$price)
print(MAPE.gbm2_train)
```

# GBM_Testing
```{r}
#Preprocessing-None
gbm_pred1_test <- predict(fit.gbm1, df_test)
gbm_pred1_test

error1.gbm <- df_test$price - gbm_pred1_test
RMSE1.gbm <- sqrt(mean(error1.gbm^2))
print(RMSE1.gbm)

#Find MAPE
MAPE.gbm1_test <- MAPE(gbm_pred1_test , y_true = df_test$price)
print(MAPE.gbm1_test)
```

```{r}
#Preprocessing-Scale & Center
gbm_pred2_test <- predict(fit.gbm1, df_test)
gbm_pred2_test

error2.gbm <- df_test$price - gbm_pred2_test
RMSE2.gbm <- sqrt(mean(error2.gbm^2))
print(RMSE2.gbm)

#Find MAPE
MAPE.gbm2_test <- MAPE(gbm_pred2_test , y_true = df_test$price)
print(MAPE.gbm2_test)
```


# RF_Training
## RF_Preproc_None
```{r}
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)
fit.rf1 <- train(price~., data=df_train,
                 method="rf", metric="RMSE", trControl=control)
print(fit.rf1)

#prediction
rf_pred1_train <- predict(fit.rf1, newdata = df_train)
print(rf_pred1_train)
#Find MAPE
MAPE.rf1_train <- MAPE(rf_pred1_train , y_true = df_train$price)
print(MAPE.rf1_train)
```


## RF_Preproc_Scale & Center
```{r}
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)
fit.rf2 <- train(price~., data=df_train,
                 method="rf", metric="RMSE", 
                 preProcess=c("center", "scale"), trControl=control)
print(fit.rf2)

#prediction
rf_pred2_train <- predict(fit.rf2, newdata = df_train)
print(rf_pred2_train)
#Find MAPE
MAPE.rf2_train <- MAPE(rf_pred2_train , y_true = df_train$price)
print(MAPE.rf2_train)
```

# RF_Testing
```{r}
#Preprocessing-None
rf_pred1_test <- predict(fit.rf1, df_test)
rf_pred1_test

error1.rf <- df_test$price - rf_pred1_test
RMSE1.rf <- sqrt(mean(error1.rf^2))
print(RMSE1.rf)

#Find MAPE
MAPE.rf1_test <- MAPE(rf_pred1_test , y_true = df_test$price)
print(MAPE.rf1_test)
```

```{r}
#Preprocessing-Scale & Center
rf_pred2_test <- predict(fit.rf2, df_test)
rf_pred2_test

error2.rf <- df_test$price - rf_pred2_test
RMSE2.rf <- sqrt(mean(error2.rf^2))
print(RMSE2.rf)

#Find MAPE
MAPE.rf2_test <- MAPE(rf_pred2_test , y_true = df_test$price)
print(MAPE.rf2_test)
```


#ARIMA

```{r}
library(tidyverse)
library(readxl)
library(forecast)
 
coal <- read_excel("Ini Dataset.xlsx")
coal$month<-as.Date(as.character(coal$month), format = "%Y-%m-%d")
 
View(coal)
 
coal%>%ggplot(aes(x=month, y=price))+geom_point()+geom_line()+ggtitle("Price Across Time")

```

```{r}
coal_train = coal[1:130,]
coal_test = coal[131:154,]
```

```{r}
coal_ts <- ts(coal$price, start = c(2009, 1), end = c(2019, 10), frequency = 12)
ArimaModel <- auto.arima((coal_ts), D=1)
summary(ArimaModel)
checkresiduals(ArimaModel)
```

```{r}
fore_arima = forecast::forecast(ArimaModel, h=24)
df_arima = as.data.frame(fore_arima)
coal_test$arima = df_arima$`Point Forecast`
mape(coal_test$price, coal_test$arima)
rmse(coal_test$price, coal_test$arima)
```

```{r}
coal_test$arima

plot(coal_test$arima,
main="ARIMA Forecasting test",
ylab="price",
type="l",
col="red")
```

```{r}
training_model <- data.frame(en_pred2_train,
                             svm_pred1_train,
                             nn_pred1_train,
                             df_train$price)

test_model <- data.frame(en_pred2_test,
                         svm_pred1_test,
                         nn_pred1_test,
                         df_test$price)
```

```{r}
write_xlsx(training_model, "C:\\Users\\Asus A409FJ\\Documents\\TA\\WADAH PIKIR\\training model.xlsx")

write_xlsx(test_model, "C:\\Users\\Asus A409FJ\\Documents\\TA\\WADAH PIKIR\\test model.xlsx")
```

# Stacking-based

```{r}
library(readxl)
df_stack <- read_excel("stacking_dataframe.xlsx")
View(df_stack)
```


```{r}
stack_train = df_stack[1:130,]
stack_test = df_stack[131:154,]

View(stack_train)
View(stack_test)
```


## Elastic Network_None_Stack
```{r}
#Elastic Net
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = TRUE)

fit.en1_stack<- train(price~., data=stack_train, method="glmnet",
                      metric="RMSE", trControl=control)
# summarize fit
print(fit.en1_stack)

#prediction
en.stack_pred1 <- predict(fit.en1_stack, newdata = stack_train)

#Find MAPE
MAPE.en.stack_pred1 <- MAPE(en.stack_pred1 , y_true = stack_train$price)
print(MAPE.en.stack_pred1)
```

## Elastic Network_Scale & Center_Stack

```{r}
#Elastic Net
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = TRUE)

fit.en2_stack<- train(price~., data=stack_train, method="glmnet",
                      metric="RMSE", preProcess=c("center", "scale"),
                      trControl=control)
# summarize fit
print(fit.en2_stack)

#prediction
en.stack_pred2 <- predict(fit.en2_stack, newdata = stack_train)

#Find MAPE
MAPE.en.stack_pred2 <- MAPE(en.stack_pred2 , y_true = stack_train$price)
print(MAPE.en.stack_pred2)
```

## Test_Elastic Network

```{r}
#Preprocessing-None
stack.en_p1_test <- predict(fit.en1_stack, stack_test)
stack.en_p1_test

mape(stack_test$price, stack.en_p1_test)
rmse(stack_test$price, stack.en_p1_test)
```

```{r}
#Scale & Center
stack.en_p2_test <- predict(fit.en2_stack, stack_test)
stack.en_p2_test

mape(stack_test$price, stack.en_p2_test)
rmse(stack_test$price, stack.en_p2_test)
```

## SVM_None_Stack

```{r}
#SVM
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)

fit.svm1_stack<- train(price~., data=stack_train, method="svmLinear3",
                      metric="RMSE", trControl=control)
# summarize fit
print(fit.svm1_stack)

#prediction
svm.stack_pred1 <- predict(fit.svm1_stack, newdata = stack_train)

#Find MAPE
MAPE.svm.stack_pred1 <- MAPE(svm.stack_pred1 , y_true = stack_train$price)
print(MAPE.svm.stack_pred1)
```

## SVM_Scale & Center_Stack

```{r}
#SVM
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)

fit.svm2_stack<- train(price~., data=stack_train, method="svmLinear3",
                       metric="RMSE", preProcess=c("center", "scale"),
                       trControl=control)
# summarize fit
print(fit.svm2_stack)

#prediction
svm.stack_pred2 <- predict(fit.svm2_stack, newdata = stack_train)

#Find MAPE
MAPE.svm.stack_pred2 <- MAPE(svm.stack_pred2 , y_true = stack_train$price)
print(MAPE.svm.stack_pred2)
```

## Test_SVM

```{r}
#Preprocessing-None
stack.svm_p1_test <- predict(fit.svm1_stack, stack_test)
stack.svm_p1_test

mape(stack_test$price, stack.svm_p1_test)
rmse(stack_test$price, stack.svm_p1_test)
```

```{r}
#Scale & Center
stack.svm_p2_test <- predict(fit.svm2_stack, stack_test)
stack.svm_p2_test

mape(stack_test$price, stack.svm_p2_test)
rmse(stack_test$price, stack.svm_p2_test)
```

## Neural Net_None_Stack

```{r}
#Neural Net
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)

fit.nn1_stack<- train(price~., data=stack_train, method="brnn",
                metric="RMSE", trControl=control)
# summarize fit
print(fit.nn1_stack)

#prediction
nn.stack_pred1 <- predict(fit.nn1_stack, newdata = stack_train)

#Find MAPE
MAPE.nn.stack_pred1 <- MAPE(nn.stack_pred1 , y_true = stack_train$price)
print(MAPE.nn.stack_pred1)
```

## Neural Net_Scale & Center_Stack

```{r}
#Neural Net
control <- trainControl(method="timeslice", initialWindow = 11, horizon = 1, fixedWindow = FALSE)

fit.nn2_stack<- train(price~., data=stack_train, method="brnn",
                metric="RMSE", preProcess=c("center", "scale"),
                trControl=control)
# summarize fit
print(fit.nn2_stack)

#prediction
nn.stack_pred2 <- predict(fit.nn2_stack, newdata = stack_train)

#Find MAPE
MAPE.nn.stack_pred2 <- MAPE(nn.stack_pred2 , y_true = stack_train$price)
print(MAPE.nn.stack_pred2)
```

## Test_Neural Net_Stack

```{r}
#Preprocessing-None
stack.nn_p1_test <- predict(fit.nn1_stack, stack_test)
stack.nn_p1_test

mape(stack_test$price, stack.nn_p1_test)
rmse(stack_test$price, stack.nn_p1_test)
```

```{r}
#Scale & Center
stack.nn_p2_test <- predict(fit.nn2_stack, stack_test)
stack.nn_p2_test

mape(stack_test$price, stack.nn_p2_test)
rmse(stack_test$price, stack.nn_p2_test)
```
